Natural Selection in the 20th Century

### 2020-10-15 why-negative-selection.Rmd
Colour changes over time in raw PGS. More work on text.

* If we weight with the GHS, and plot the means of figure 1 using this w
  weighting, most things stay the same - but the change in EA is reversed! EA
  increases over time. Could this be because the sample includes many
  relatively educated older people? If so, then mean effects are *overestimated*
  by figure 1. 
* Reweight other regressions (e.g. the omnibus regression in the appendix)
* Look at geography, esp. in siblings regressions.
* control for age in n_partners regressions.
* Beauchamp 2016 used the HRS. He reckons it's representative. Is it? How do
  his effect sizes compare?
  - he also worries about the quality/quantity tradeoff, which might mean that
    people with fewer children have more grandchildren (than you'd expect). 
    As we have the two generations, we can test this. (Actually, there's a 
    positive correlation of about 0.1)

@@

```{r calc-means-over-time}

drake::loadd(famhist)

pgs_over_time <- famhist %>% 
      group_by(
        YOB = santoku::chop(YOB, 
          seq(1940, 1970, 5), 
          labels    = seq(40, 65, 5),
          extend    = FALSE
        ) 
      ) %>% 
      filter(! is.na(YOB)) %>% 
      summarize(across(all_of(score_names), ggplot2::mean_cl_normal, na.rm = TRUE)) %>% 
      pivot_longer(-YOB, names_to = "score_name", values_to = "score") %>% 
      mutate(
        score_lo = score$ymin,
        score_hi = score$ymax,
        score    = score$y
      )

@@

Figure \@ref(fig:plot-means-over-time) plots mean polygenic scores by 5-year
birth intervals, for the entire sample. Several scores show consistent increases
or declines over this 30-year period, of the order of 5% of a standard deviation.

```{r plot-means-over-time, fig.height = 5, fig.cap = "Mean polygenic scores by birth year in UK Biobank. Points are means for 5-year intervals. Lines are 95% confidence intervals."}

pgs_over_time %>% 
      mutate(score_name = pretty_names(score_name)) %>% 
      ggplot(aes(YOB, group = score_name)) + 
      geom_pointrange(aes(ymin = score_lo, y = score, ymax = score_hi), 
        colour = "steelblue4", fatten = 2) +
      facet_wrap(~score_name) +
      my_hline +
      theme(
        strip.text  = element_text(size = 6), 
        axis.text.x = element_text(size = 7)
      ) +
      labs(y = "PGS", x = "Birth year (5 year intervals)")

These estimates may suffer from ascertainment bias within the UK Biobank sample.
Respondents are higher income and better educated than the UK population, and
they may also differ on other unobserved characteristics [@10.1093/aje/kwx246].

To examine the effects of sampling, we start by measuring the strength of
natural selection within different subgroups. To do this we regress respondents' 
polygenic scores on their number of children:

@@

The effect size $\beta$ measures the strength of natural selection within the
sample (or a given subgroup). In fact, since polygenic scores are normalized to
mean 0, $\beta$ is the expected polygenic score among children of the sample or
subgroup.

Figures \@ref(fig:plot-educ-level) and \@ref(fig:plot-income) plot effect sizes
for each polygenic score. Figure \@ref(fig:plot-educ-level) groups respondents
by age of completing full-time education. Figure \@ref(fig:plot-income) groups
respondents by household income. Effect sizes are larger and more significant
for the lowest income category, and for the lowest education category. Note that
the overall effect is not a simple average of the effect among the different
subgroups, because polygenic scores may also shift respondents between the
subgroups. For example, a high PGS for educational attainment may increase the
age at which a respondent leaves school.

@@

When we split respondents up by other demographic variables, we get a more
surprising result: the direction of natural selection is different among
different subgroups.

Figure \@ref(fig:plot-age-flb-cross) shows effect sizes estimated separately for
each tercile of age at first live birth. Several effects are strikingly
different across terciles. ADHD and MDD are selected for amongst the youngest
third of mothers, but selected against among the oldest two-thirds. Educational
attainment is selected for among the oldest two-thirds of mothers, but is not
significantly selected among the youngest third. Similarly, several PGS of body
measurements are selected against only among older mothers. The correlation
between effect sizes for the youngest and oldest terciles is `r cor_age_flb`.

Figure \@ref(fig:plot-n-partners) splits males and females by lifetime number of
sexual partners, at the median value of 3. Again, selection effects are reversed
across the groups. Among men and women with more than 3 sexual partners, for
example, educational attainment is selected against; among those with 3 or fewer
sexual partners, it is selected for.

Figure \@ref(fig:plot-with-partner) splits respondents up by whether they
were living with a spouse or partner at the time of interview. Effects are 
generally the same sign in both groups, but are much larger among those not
living with a spouse or partner.

@@

drake::loadd(res_partners)
res_partners %<>%       
      filter(term != "(Intercept)", term != "lo_partnersTRUE") %>% 
      mutate(`N partners` = ifelse(grepl(":", term), "<= 3", "> 3"))

@@

@@

Figure \@ref(fig:plot-age-flb) shows the results of regressions for women only,
controlling for age at first live birth. Effect sizes are greatly reduced.
This could be because the regressions exclude childless women. However, in 
`r opp_signed` out of `r length(score_names)` cases, effects actually change
sign when controls are added. The correlation between effect sizes controlling for age
at first live birth, and raw effect sizes, is `r cor_raw_flb`.

@@

res_wt_combined <- bind_rows(
  None                     = res_all %>% 
                               filter(reg.type == "raw", dep.var == "N children") %>% 
                               select(-reg.type, -dep.var, -score_name),
  Geographical             = res_wt_msoa_weights,
  `Age/Qualification`      = res_wt_age_qual_weights,
  `Age/Qual/FLB`  = res_wt_flb_weights,
  .id = "Weights"
)

@@

rel_sizes <- res_wt_cb_wide %>% 
                filter(
                  consistent, 
                  p.value < 0.05/length(score_names)
                ) %>% 
                mutate(
                  Geographical = Geographical/None,
                  `Age/Qualification` = `Age/Qualification`/None,
                  `Age/Qual/FLB` = `Age/Qual/FLB`/estimate_females
                ) %>% 
                select(-consistent, -None, -p.value, -estimate_females) %>% 
                mutate(
                  term = pretty_names(term)
                )

@@

To compensate for ascertainment bias in the UK Biobank sample, we weight 
participants using data from the 2011 Census and from the 2006 General Household
Survey (GHS). We try three alternative weighting schemes:

@@

Figure \@ref(fig:plot-res-wt) plots effect sizes among the entire sample, using
these weighting schemes. We include unweighted regressions for comparison.
Weighted effect sizes are significantly larger in absolute value. Table
\@ref(tab:tbl-res-wt) gives effect sizes as a proportion of unweighted effect
sizes for the census-based weightings.

Effect sizes are reasonably consistent across the geographical and
age/qualification weights, but they are increased again when we weight by age at
first live birth. This suggests that estimates might be further affected by
weighting on other demographic variables. Given that the Biobank sample
seems to be ascertained in ways that reduce estimates of natural selection, 
we view our estimates as likely to be conservative.

@@

rel_sizes %>% 
      arrange(desc(Geographical)) %>% 
      bind_rows(rel_sizes_summary) %>% 
      rename(PGS = term) %>% 
      as_hux() %>% 
      insert_row("", "Weighting", fill = "") %>% 
      set_caption(
        "Weighted effect sizes as a proportion of unweighted"
      ) %>% 
      merge_cells(1, 2:4) %>% 
      set_align(1, 2, "centre") %>% 
      set_header_rows(1, TRUE) %>% 
      theme_compact() %>% 
      style_headers(bold = TRUE) %>% 
      set_bottom_border(1, 2:4) %>% 
      set_bottom_border(2, everywhere) %>% 
      set_italic(final(2), 1) %>% 
      set_font_size(8) %>% 
      set_width(0.7) %>% # ensures line wrapping below
      set_col_width(c(.34, .22, .22, .22)) %>% 
      add_footnote(paste0(
        "Only consistent and significant (when unweighted) estimates ",
        "are shown.\n",
        "Age/Qual/FLB as a proportion of unweighted regressions ",
        "for females only."),
        font_size    = 6, 
        top_padding  = 0,
        left_padding = 0
      )

@@

Why do selection effects have *opposite* signs across certain subgroups -- for
example, across older and younger mothers by age at first live birth, or across those
with more and fewer lifetime sexual partners? A possible answer is given by the
economic theory of fertility [@becker1960economic]. According to this,
increases in potential earned income affect fertility via two opposing channels.
There is an "income effect" by which children become more affordable, like any
other good. Since childrearing has a cost in time, there is also a substitution
effect: the opportunity cost of childrearing increases if one's market wage is
higher. The income effect would lead higher earners to have more children. The
substitution effect would lead higher earners to have fewer children. It is
often assumed that the substitution effect will dominate for lone parents, since
they have less opportunity to share childcare responsibilities, while the income
effect will dominate for couples who are able to reap the gains from
specialization.

If so, then genetic characteristics which affect one's earnings potential in the
labour market may lead to opposing effects on fertility. Genetic
variants which improve one's earnings may increase fertility among couples, but
decrease fertility among single parents. They may also decrease the likelihood
of becoming a young mother, if this is correlated with single motherhood. Lastly,
if lifetime number of sexual partners predicts single parent versus 
two-parent status, the theory could also explain the differently-signed
effects across people with more and fewer sexual partners.

This explanation predicts that the strength of polygenic scores' effects on
fertility will correlate with the strength of their relationship with earnings.
We measure the correlation of each PGS with household income, as well as with
education level, a phenotype which predicts earnings. We
then relate these measurements to effect sizes on number of children.
There is a clear negative relationship between a score's effect on
fertility, and its correlation with income or education (Figure \@ref(fig:plot-cors-income-educ)). If we control for age at first live birth,
the relationship changes sign and becomes positive.

@@

Natural selection is taking place in modern populations on variants underlying
many polygenic scores. In a loose sense, phenotypes relating to scores which are
selected for (against) would be seen as undesirable (desirable) by many people.
For example, most people would probably prefer to have high educational
attainment, a low risk of major depressive disorder, and a low risk of coronary
artery disease, but PGS underlying these traits are being selected for.
Potentially, natural selection could increase the health burden on modern
societies, but that depends on effect sizes. Existing work argues that these are
small. However, as we show, estimates can be crucially affected by ascertainment
bias in population samples. In addition, we do not know whether estimated effect
sizes of natural selection will increase or decrease as more accurate polygenic
scores are produced. We are also unsure about whether polygenic scores for new
phenotypes will show a similar pattern of natural selection as existing ones. In
short, it is probably too early to tell whether modern natural selection is
substantively important or not.

Previous work has documented natural selection in modern populations
[@beauchamp2016genetic; @kong2017selection; @sanjak2018evidence] but has not
explained its underlying causes. The economic theory of fertility provides a
parsimonious explanation for which traits are selected, and for why the
direction of selection is reversed among certain subgroups. An alternative
theory is that traits selected for are linked to impulsivity and low time
discount rates, via the channel of early sexual behaviour. The data here provide
some support for this: scores which might plausibly be linked to
impulsivity,like ADHD and age at smoking initiation, are selected for. However,
the "impulsivity" theory is less good at explaining variation in selection
across the full range of scores, including e.g. waist-hip ratio and BMI.
Impulsivity also does not explain the reversed sign of selection among e.g.
older parents. Overall, then, the economic theory is probably the leading
explanation at present.

@@

>>>>

* If we weight with the GHS, and plot the means of figure 1 using this w
  weighting, most things stay the same - but the change in EA is reversed! EA
  increases over time. Could this be because the sample includes many
  relatively educated older people? If so, then mean effects are *overestimated*
  by figure 1. 
* Reweight other regressions (e.g. the omnibus regression in the appendix)
* Look at geography, esp. in siblings regressions.
* Beauchamp 2016 used the HRS. He reckons it's representative. Is it? How do
  his effect sizes compare?
  - he also worries about the quality/quantity tradeoff, which might mean that
    people with fewer children have more grandchildren (than you'd expect). 
    As we have the two generations, we can test this. (Actually, there's a 
    positive correlation of about 0.1)

@@

We first show raw changes in polygenic scores over birth years, within the entire UK Biobank
sample. Figure \@ref(fig:plot-means-over-time) plots mean polygenic scores by 5-year
birth intervals. Several scores show consistent increases or declines over this 
30-year period, of the order of 5% of a standard deviation.

```{r plot-means-over-time, fig.height = 5, fig.cap = "Mean polygenic scores by birth year in UK Biobank. Points are means for 5-year intervals. Lines are 95% confidence intervals. Green lines show a significant increase over time (p < 0.05). Red lines show a significant decrease."}

drake::loadd(pgs_over_time)

pgs_over_time %>% 
      mutate(score_name = pretty_names(score_name)) %>% 
      ggplot(aes(YOB, group = score_name, colour = Change)) + 
      geom_pointrange(aes(ymin = score_lo, y = score, ymax = score_hi), 
        fatten = 2) +
      facet_wrap(~score_name, ncol = 5) +
      my_hline +
      scale_color_manual(values = c("-" = "red", "+" = "darkgreen", "o" = "black")) +
      theme(
        strip.text  = element_text(size = 6), 
        axis.text.x = element_text(size = 7),
        legend.position = "none"
      ) +
      labs(y = "PGS", x = "Birth year (5 year intervals)")

@@

These changes could reflect either natural selection within the UK population,
or ascertainment bias within the sample. 
Respondents are higher income and better educated than the UK population, and
they may also differ on other unobserved characteristics [@10.1093/aje/kwx246].
Since richer and educated people also live longer, this bias might also increase
with age.

To examine the effects of sampling, we start by measuring the strength of
natural selection within different subgroups. To do this we regress respondents' 
polygenic scores on their number of children ($y_i$):

@@

```{r calc-sex-ratio}
female_ratio <- mean(famhist$sex == 0)
```

The effect size $\beta$ measures the strength of natural selection within the
sample or a given subgroup. In fact, since polygenic scores are normalized to
mean 0, $\beta$ is the expected polygenic score among children of the sample or
subgroup [@beauchamp2016genetic]. We begin with basic demographic variables
including education, income and sex. These are all potential sources of ascertainment
bias: as well as the ascertainment for income and education, mentioned above, the
sample sex ratio  skews `r female_ratio * 100`% female.

Figures \@ref(fig:plot-educ-level) and \@ref(fig:plot-income) plot effect sizes
for each polygenic score. Figure \@ref(fig:plot-educ-level) groups respondents
by age of completing full-time education. Figure \@ref(fig:plot-income) groups
respondents by household income. Effect sizes are larger and more significant
for the lowest income category, and for the lowest education category. Note that
the overall effect is not a simple average of the effect among the different
subgroups, because polygenic scores may also shift respondents between the
subgroups. For example, a high PGS for educational attainment may correlate
with fewer children among early school leavers, but may also increase the
age at which a respondent leaves school.

@@

These results show that ascertainment within UK Biobank could bias estimates
of the size of natural selection towards zero. We now focus in on variables 
specifically related to marriage markets and raising children. Whatever processes 
give rise to natural selection, these variables are likely to be involved; at
the same time, they may also be ascertained within the sample.

Figure \@ref(fig:plot-n-partners) splits males and females by lifetime number of
sexual partners, at the median value of 3. For both sexes, effects are larger
and more significant among those with more than 3 partners. Results are
unchanged if we control for respondents' age (Figure
\@ref(fig:plot-n-partners-controlled) in the appendix). Figure
\@ref(fig:plot-with-partner) splits respondents up by whether they were living
with a spouse or partner at the time of interview. Again, effects are larger
among those not living with a spouse or partner.

@@

drake::loadd(res_partners)
res_partners %<>%       
      filter(grepl(":", term)) %>% 
      mutate(`N partners` = ifelse(grepl("TRUE:", term), "<= 3", "> 3"))

@@

Our final variable is age at first live birth (AFLB), for females only. There is evidence
for genetic effects on AFLB [@Barban_2016]. There is also 
a close link between this variable and number of children born.

Figure \@ref(fig:plot-age-flb-cross) shows effect sizes estimated separately for
each tercile of AFLB. Several effects are strikingly
different across terciles. ADHD and MDD are selected for amongst the youngest
third of mothers, but selected against among the oldest two-thirds. Educational
attainment is selected for among the oldest two-thirds of mothers, but is not
significantly selected among the youngest third. Similarly, several PGS of body
measurements are selected against only among older mothers. The correlation
between effect sizes for the youngest and oldest terciles is `r cor_age_flb`.
As before, recall that PGS may have two effects: they may change the number of
children within categories, but may also shift respondents between categories.

@@

To investigate this further, we regress number of children on PGS *controlling*
for AFLB. Figure \@ref(fig:plot-age-flb) shows the results, along with raw
effect sizes for comparison. Controlling for AFLB greatly reduces effect sizes.
This could be because the controlled regressions exclude childless women.
However, in `r opp_signed` out of `r length(score_names)` cases, effects
actually change sign when controls are added. The correlation between effect
sizes controlling for AFLB, and raw effect sizes, is `r cor_raw_flb`. So,
natural selection "effects" seem to come through two channels: an effect on
AFLB, and an effect on number of children controlling for AFLB. Moreover, these
channels often push in opposite directions.

@@

res_wt_combined <- bind_rows(
  None                     = res_all %>% 
                               filter(reg.type == "raw", dep.var == "N children") %>% 
                               select(-reg.type, -dep.var, -score_name),
  Geographical             = res_wt_msoa_weights,
  `Age/Qualification`      = res_wt_age_qual_weights,
  `Age/Qual/AFLB`  = res_wt_flb_weights,
  .id = "Weights"
)

@@

rel_sizes <- res_wt_cb_wide %>% 
                filter(
                  consistent, 
                  p.value < 0.05/length(score_names)
                ) %>% 
                mutate(
                  Geographical = Geographical/None,
                  `Age/Qualification` = `Age/Qualification`/None,
                  `Age/Qual/AFLB` = `Age/Qual/AFLB`/estimate_females
                ) %>% 
                select(-consistent, -None, -p.value, -estimate_females) %>% 
                mutate(
                  term = pretty_names(term)
                )

@@

These results show that there may be ascertainment bias in estimates of natural
selection derived from UK Biobank. One way to compensate for this is by survey
weighting. Weighting is not guaranteed to lead to unbiased estimates, because as
well as ascertainment on characteristics which we measure and weight for, there
may also be ascertainment on other, unmeasured characteristics. But the exercise
will give us a rough sense of the direction and magnitude of bias. We weight
participants using data from the 2011 Census and from the 2006 General Household
Survey (GHS). We try three alternative weighting schemes:

@@

Figure \@ref(fig:plot-res-wt) plots effect sizes among the entire sample, using
these weighting schemes. We include unweighted regressions for comparison. Table
\@ref(tab:tbl-res-wt) gives effect sizes as a proportion of the unweighted
effect size. As expected, weighting generally increases estimated effect sizes.
Sizes are reasonably similar across the geographical and age/qualification
weights, but they are increased further when we weight by AFLB. This suggests
that estimates might be further affected by weighting on other demographic
variables. Given that the Biobank sample seems to be ascertained in ways that
reduce estimates of natural selection, we suspect that these weighted estimates
are still conservative.

@@

rel_sizes %>% 
      arrange(desc(Geographical)) %>% 
      bind_rows(rel_sizes_summary) %>% 
      rename(PGS = term) %>% 
      as_hux() %>% 
      insert_row("", "Weighting", fill = "") %>% 
      set_caption(
        "Weighted effect sizes as a proportion of unweighted"
      ) %>% 
      merge_cells(1, 2:4) %>% 
      set_align(1, 2, "centre") %>% 
      set_header_rows(1, TRUE) %>% 
      theme_compact() %>% 
      style_headers(bold = TRUE) %>% 
      set_bottom_border(1, 2:4) %>% 
      set_bottom_border(2, everywhere) %>% 
      set_italic(final(2), 1) %>% 
      set_font_size(8) %>% 
      set_width(0.7) %>% # ensures line wrapping below
      set_col_width(c(.34, .22, .22, .22)) %>% 
      add_footnote(paste0(
        "Only consistent and significant (when unweighted) estimates ",
        "are shown.\n",
        "Age/Qual/AFLB as a proportion of unweighted regressions ",
        "for females only."),
        font_size    = 6, 
        top_padding  = 0,
        left_padding = 0
      )

@@

Why do selection effects have *opposite* signs across older and younger mothers at first live birth, and opposite signs when AFLB is controlled for? A possible answer is given by the
economic theory of fertility [@becker1960economic]. According to this,
increases in potential earned income affect fertility via two opposing channels.
There is an "income effect" by which children become more affordable, like any
other good. Since childrearing has a cost in time, there is also a substitution
effect: the opportunity cost of childrearing increases if one's market wage is
higher. The income effect would lead higher earners to have more children. The
substitution effect would lead higher earners to have fewer children. It is
often assumed that the substitution effect will dominate for lone parents, since
they have less opportunity to share childcare responsibilities, while the income
effect will dominate for couples who are able to reap the gains from
specialization.

If so, then genetic characteristics which affect one's earnings potential in the
labour market may lead to opposing effects on fertility. Genetic
variants which improve one's earnings may increase fertility among couples, but
decrease fertility among single parents. They may also decrease the likelihood
of becoming a young mother, if this is correlated with single motherhood. Lastly,
if lifetime number of sexual partners predicts single parent versus 
two-parent status, the theory could also explain the different
effect sizes across people with more and fewer sexual partners.

This explanation predicts that the strength of polygenic scores' effects on
fertility will correlate with the strength of their relationship with earnings.
To test this, we measure the correlation of each PGS with household income, 
as well as with education level, a phenotype which predicts earnings. We
then relate these measurements to effect sizes on number of children.
There is a clear negative relationship between a score's effect on
fertility, and its correlation with income or education (Figure \@ref(fig:plot-cors-income-educ)). If we control for age at first live birth,
the relationship changes sign and becomes positive.

@@

Natural selection is taking place in modern populations on variants underlying
many polygenic scores. In a loose sense, phenotypes relating to scores which are
selected for (against) would be seen as undesirable (desirable) by many people.
For example, most people would probably prefer to have high educational
attainment, a low risk of major depressive disorder, and a low risk of coronary
artery disease, but PGS underlying these traits are being selected for. In addition,
the size of selection on PGS is negatively correlated with the score's correlation 
with household income. Potentially, natural selection could increase the health 
burden on modern societies, but that depends on effect sizes. Existing work 
argues that these are small [@beauchamp2016genetic].

However, as we show, estimates can be crucially affected by ascertainment
bias in population samples. This problem may be less serious in other surveys,
such as the US Health and Retirement Study, which explicitly aims to be
representative (as the UK Biobank does not). Nevertheless, ascertainment bias 
can still be a problem, since not all respondents consent to the collection of
genetic data: for instance, completion rates were around 80-85% for HRS genotype
data [@hrs2020].

In addition, we do not know whether estimated effect sizes of natural selection
will increase or decrease as more accurate polygenic scores are produced. We are
also unsure about whether polygenic scores for new phenotypes will show a
similar pattern of natural selection as existing ones. In short, it is probably
too early to tell whether modern natural selection is substantively important or
not.

Previous work has documented natural selection in modern populations
[@beauchamp2016genetic; @kong2017selection; @sanjak2018evidence] but has not
explained its underlying causes. The economic theory of fertility provides a
parsimonious explanation for which traits are selected, and for why the
direction of selection is reversed among certain subgroups. An alternative
theory is that traits selected for are linked to externalizing behaviour and low
time discount rates, via the channel of early sexual behaviour
[@Mills2020.05.06.081273]. The data here provide some support for this: scores
which might plausibly be linked to externalizing behaviour, like ADHD and age at
smoking initiation, are selected for. However, this theory is less
good at explaining variation in selection across the full range of scores,
including for example waist-hip ratio and BMI. Externalizing behaviour also does 
not explain the reversed sign of selection among older parents. Overall, 
we believe that the economic theory is the leading explanation at present.

@@

## Selection by number of partners, controlling for age

Figure \@ref(fig:plot-n-partners-controlled) shows selection effects by
lifetime number of sexual partners. Age, age squared, and interactions of 
age and age squared with PGS are controlled for.

```{r plot-n-partners-controlled, fig.cap = "Effect sizes on number of siblings interacted with number of sexual partners (median split at 3), respondent's age and age squared."}
drake::loadd(res_partners_controlled)
res_partners_controlled %<>%       
      filter(term != "(Intercept)", term != "lo_partnersTRUE") %>% 
      mutate(`N partners` = ifelse(grepl("TRUE:", term), "<= 3", "> 3"))

n_regs <- as.double(nrow(res_partners_controlled))
res_partners_controlled %>% 
      mutate(
        score_name = pretty_names(score_name)
      ) %>% 
      ggplot(aes(
        y      = reorder_within(score_name, estimate, sex, fun = order_abs(1)), 
        x      = estimate, 
        fill   = `N partners`, 
        colour = p.value < 0.05/{{n_regs}}
      )) + 
        my_vline +
        pval_geom_point() +
        facet_wrap(vars(sex), scales = "free_y") +
        my_fill_scale(n = 2) +
        pval_scale() +
        my_theme(legend.position = "bottom") +
        my_labs(x = "", y = "") + 
        scale_y_reordered()
